Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Updated Figure 9

```{r}
#| label: fig-rm-lg
#| fig-cap: "XXX Shouldn't the middle one have an edge connecting inside a C, so that it is clearly not as good as c? XXX Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 2.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15

>>>>

```{r}
#| label: fig-rm-lg
#| fig-cap: "XXX Shouldn't the middle one have an edge connecting inside a C, so that it is clearly not as good as c? XXX Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 6.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15
